\section{Scenarios}
\textbf{Christian}:
It is Thursday evening and Christian has taken his board game under his arm, like he does every Thursday and mounted his bike. Before he hits Thomas's house, he bikes towards Netto to get ready for a long evening. However, he thinks it's annoying to drag the game through Netto and in addition, it also limits the amount of supplies he can carry on his bike. When Christian arrives at Thomas and opens the game box, he can see how all the cards are messed up after the bike ride, after a while they have finally got all the content of the box sorted and can start playing. After playing for a while, a friend makes an unauthorized move, which is first discovered later. This move annoys Christian, as this will have an impact on the outcome of the game. Late in the evening they will have to stop the game as they go to school the next day and have to write down how far they have come.

\textbf{Lærke}:
It is Friday evening and Lærke can not afford to go out to town. Instead, she opens her tablet and finds the "Play store" to find a new co-op game she can play with her Danish friends. She finds the game "BackFight". Lærke writes to her Danish friends if they want to play with her. They quickly download the game and start a game. Time flies away and they are doing their second game, unfortunately, they have to stop when one of them need to wake up early the next day. The following day, they all want to continue the game. They open the app and choose their game from the day before and can continue from where they stopped.
